---
title: "Exercise 01-b"
format: html
editor: visual
---

## Exercise 1b.

### Sampling from log-normal distribution

First, we draw 100 samples from a log-normal distribution with mean 5 and standard deviation = 0.5.

The seed is chosen to ensure the reproducibility of the results.

```{r}
set.seed(42)
sample <- rlnorm(100, meanlog = 5, sdlog = 0.5)
sample_df <- data.frame(sample)

```

### Create the histogram using ggplot2 package

First, load ggplot2:

```{r}
library(ggplot2)
```

Then, create a histogram using the geom_histogram() function. For the **linear** scale, we just plot the samples we obtained in *sample*.

```{r}
linear_histogram <- ggplot(sample_df, aes(x=sample)) + geom_histogram(binwidth=10) + ggtitle("Histogram in linear scale") + xlab("sample value") + ylab("frequency")


linear_histogram
```

For the **log** scale, we will apply a *log* to the samples column in the data frame. We will also customize the histogram.

```{r}

log_histogram <- ggplot(sample_df, aes(x=log(sample))) + geom_histogram(color="black", fill="white") + ggtitle("Histogram in log scale") + xlab("log(sample value)") + ylab("frequency")

log_histogram
```

### Create a violin plot with ggplot2

```{r}
violin_plot <- ggplot(sample_df, aes(x="", y=sample)) + geom_violin() + ggtitle("Violin plot in linear scale") + ylab("Values")
violin_plot

log_violin_plot <- ggplot(sample_df, aes(x="", y=log(sample))) + geom_violin(fill="#E69F00") + ggtitle("Violin plot in log scale") +ylab("Values") + xlab("")
log_violin_plot
```

### Reporting the mean and the standard deviation

The mean of the sampled values is `r round(mean(sample), digits = 2)`, and the standard deviation is `r round(sd(sample), digits = 2)`
